Raising the role of Vocabulary Hubs for Semantic data interoperability in Dataspaces

### 2024-06-12 EBDVF-2024/paper.qmd
Added project uris and line breaks

# Projects and Use Cases
In the expanding data economy landscape supported by data spaces, we are working in several projects which address the practical needs and were we experience the importance of semantic interoperability to fulfill various use cases. Here we present 3 examples of from the DataBri-X and UNDERPIN projects, which cover various application domains.

@@

Both GraphDb and PoolParty are based on W3C recommendations like RDF, OWL and SPARQL. They therefore seamlessly integrate with each other, but also with other services and components in data spaces which support these machine-readable standards for semantic interoperability.

The Wind Farm Ontology [@ikeresnaola-gonzalezWindFarmOntology2021] ...

>>>>

# Projects and Use Cases
In the expanding data economy landscape supported by data spaces, we are working in several projects which address the practical needs
and were we experience the importance of semantic interoperability to fulfill various use cases.
Here we present 3 examples of from the [DataBri-X](https://databri-x.eu/) and [UNDERPIN](https://underpinproject.eu/) projects,
which cover various application domains.

@@

Both GraphDB and PoolParty are based on W3C recommendations like RDF, OWL and SPARQL.
They therefore seamlessly integrate with each other, but also with other services and components in data spaces which support
these machine-readable standards for semantic interoperability.
